---
title: Representation Analysis
author:
  - name: Liang Zhang
  - name: Jintao Sheng
format:
  html:
    code-fold: true
    toc: true
execute:
  warning: false
editor_options:
  chunk_output_type: console
---

```{r}
#| label: setup
#| warning: false
#| message: false

library(tidyverse)
library(patchwork)
invisible(common::source.all("R_quarto", isolate = FALSE))
theme_set(
  ggpubr::theme_pubr(base_family = "Gill Sans MT", base_size = 12) %+replace%
    theme(
      axis.line = element_line(linewidth = 1),
      # to make the background transparent
      # by ChatGPT: based on https://stackoverflow.com/a/41878833/5996475
      panel.background = element_rect(fill = "transparent", colour = NA),
      plot.background = element_rect(fill = "transparent", colour = NA),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.key = element_rect(fill = "transparent", colour = NA)
    )
)
```

# Behavioral Results

## Main Results

```{r}
#| label: fig-1-behav
#| fig-width: 8
#| fig-height: 5

layout <- "
###AA
###AA
###BB
CCCBB
CCCDD
CCCDD
"

p_perf <- targets::tar_read(mem_perf) |>
  ggplot(aes(dprime)) +
  geom_histogram(fill = "grey") +
  scale_x_continuous(name = "d' (Overall)") +
  scale_y_continuous(name = "Count")

p_smc <- targets::tar_read(smc) |>
  enframe() |>
  ggplot(aes(value)) +
  geom_histogram(fill = "grey") +
  scale_x_continuous(name = "SMC") +
  scale_y_continuous(name = "Count")

p_memorability <- targets::tar_read(memorability) |>
  filter(word_id <= 150) |>
  mutate(
    trial_id_new = as.integer(fct_reorder(factor(trial_id), desc(pc)))
  ) |>
  ggplot(aes(trial_id_new, ymin = 0, ymax = pc)) +
  geom_linerange(color = "grey", linewidth = 0.7) +
  scale_x_continuous(name = "Order of Words", expand = expansion(add = 0.5)) +
  scale_y_continuous(name = "Memorability", expand = c(0, 0))

p_memorability_content <- targets::tar_read(memorability_content) |>
  ggplot(aes(r)) +
  geom_histogram(fill = "grey") +
  geom_vline(
    xintercept = mean(targets::tar_read(memorability_content)$r),
    linetype = "dotted"
  ) +
  geom_vline(xintercept = sqrt(0.5), linetype = "dotted", color = "red") +
  scale_x_continuous(
    name = "Individual-to-Group\nMemory Content Similarity"
  ) +
  scale_y_continuous(name = "Count", expand = expansion(c(0, 0)))

p_perf +
  p_smc +
  p_memorability +
  p_memorability_content +
  plot_layout(design = layout)

if (!interactive()) {
  ggsave_default(width = 8, height = 5)
}
```

## Supplementary Results

```{r}
#| label: fig-supp-1-behav-corr
#| fig-width: 6
#| fig-height: 6

targets::tar_read(mem_perf) |>
  left_join(
    targets::tar_read(mem_perf_precise),
    by = "subj_id"
  ) |>
  select(!subj_id) |>
  rename(
    Overall = dprime,
    Recollection = dprime_rem,
    Familiarity = dprime_know
  ) |>
  GGally::ggpairs(
    diag = list(continuous = "barDiag"),
    lower = list(
      continuous = function(data, mapping, ...) {
        ggplot(data, mapping) +
          geom_point(color = "grey") +
          geom_smooth(method = "lm", color = "black") +
          ggpmisc::stat_correlation(
            ggpmisc::use_label(c("r", "p.value")),
            small.r = TRUE,
            small.p = TRUE
          )
      }
    ),
    upper = "blank",
    switch = "both"
  ) +
  theme(
    strip.text = element_text(size = 16),
    strip.background = element_blank(),
    strip.placement = "outside"
  )

if (!interactive()) {
  ggsave_default(width = 6, height = 6)
}
```

# Representation Stability

Here we investigate the stability of group-level representations across participants. We compute the stability of group-level representations by randomly sampling a subset of participants and computing the correlation between the group-level representation computed from this subset and the full group-level representation.

See [this quarto document](./_topoplot.qmd) for the topography of CCA components (first 3 only).

```{r}
#| label: fig-supp-2-group-averaged-stability
#| fig-width: 6
#| fig-height: 4

targets::tar_load(patterns_group_stability)
size_subjs <- seq(20, 200, by = 20)
predictions <- patterns_group_stability |>
  reframe(
    fit_curve(size, r) |>
      predict(newdata = data.frame(x = size_subjs)) |>
      as_tibble_col("r") |>
      add_column(size = size_subjs, .before = 1L),
    .by = cca_id
  )
p_stability <- patterns_group_stability |>
  ggplot(aes(size, r, color = factor(cca_id))) +
  ggdist::stat_dotsinterval() +
  geom_point(aes(size, r), predictions, size = 1) +
  geom_line(aes(size, r), predictions, linetype = "longdash") +
  scale_x_continuous(
    name = "# Participants",
    breaks = scales::breaks_width(40)
  ) +
  scale_y_continuous(name = "Stability") +
  scale_color_components() +
  facet_grid(cols = vars(cca_id), scales = "free") +
  theme(strip.text = element_blank())

p_trend_gss <- targets::tar_read(data_gss_whole_resampled) |>
  ggplot(aes(size, gss, color = factor(cca_id))) +
  ggdist::stat_dotsinterval() +
  scale_x_continuous(
    name = "# Participants",
    breaks = scales::breaks_width(40)
  ) +
  scale_y_continuous(name = "GSS") +
  scale_color_components(guide = "none") +
  facet_grid(cols = vars(cca_id), scales = "free") +
  theme(strip.text = element_blank())

p_stability /
  p_trend_gss +
  plot_layout(guides = "collect", axes = "collect") &
  theme(legend.position = "bottom")

if (!interactive()) {
  ggsave_default(width = 6, height = 4)
}
```

# Semantic transformation, representation fidelity, and memory

Here we use individual to semantic representation similarity (ISS), indicating *semantic transformation*, and individual to group representation similarity (IGS), indicating *representation fidelity*, to predict memory performance. We also compare the predictive power of ISS and IGS, retain the mediation analysis for reference, and quantify their unique and shared contributions to memory performance.

## Predictive power of ISS and IGS (overall d')

```{r}
#| label: fig-2-iss-igs-pred-mem
#| fig-width: 13
#| fig-height: 8

# ISS predicts memory
# show legend because this the first panel of the figure
p_iss_mem_scatter <- visualize_scatter(
  targets::tar_read(data_iss_whole),
  targets::tar_read(mem_perf),
  show_legend = TRUE
)

p_iss_mem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iss_mem_dynamic),
  targets::tar_read(clusters_stats_iss_mem_dynamic),
  col_stat = "estimate",
  lab_stat = expression(italic(r)[ISS - "d'"])
)

# IGS predicts memory
p_igs_mem_scatter <- visualize_scatter(
  targets::tar_read(data_igs_whole),
  targets::tar_read(mem_perf)
)

p_igs_mem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_igs_mem_dynamic),
  targets::tar_read(clusters_stats_igs_mem_dynamic),
  lab_stat = expression(italic(r)[IGS - "d'"])
)

(p_iss_mem_scatter | p_iss_mem_dynamic) /
  (p_igs_mem_scatter | p_igs_mem_dynamic) +
  plot_layout(guides = "collect") &
  # tags are added in Adobe Illustrator
  # plot_annotation(tag_levels = "A") &
  theme(legend.position = "top")

if (!interactive()) {
  ggsave_default(width = 13, height = 5)
}
```

```{r}
#| label: fig-supp-X-iss-igs-pred-mem-rt-locked
#| fig-width: 13
#| fig-height: 8

# ISS predicts memory
# show legend because this the first panel of the figure
p_iss_mem_scatter <- visualize_scatter(
  targets::tar_read(data_iss_whole_rt_locked),
  targets::tar_read(mem_perf),
  show_legend = TRUE
)

p_iss_mem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iss_mem_dynamic_rt_locked),
  targets::tar_read(clusters_stats_iss_mem_dynamic_rt_locked),
  col_stat = "estimate",
  lab_stat = expression(italic(r)[ISS - "d'"]),
  onset = 1
)

# IGS predicts memory
p_igs_mem_scatter <- visualize_scatter(
  targets::tar_read(data_igs_whole_rt_locked),
  targets::tar_read(mem_perf)
)

p_igs_mem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_igs_mem_dynamic_rt_locked),
  targets::tar_read(clusters_stats_igs_mem_dynamic_rt_locked),
  lab_stat = expression(italic(r)[IGS - "d'"]),
  onset = 1
)

(p_iss_mem_scatter | p_iss_mem_dynamic) /
  (p_igs_mem_scatter | p_igs_mem_dynamic) +
  plot_layout(guides = "collect") +
  # tags are added in Adobe Illustrator
  # plot_annotation(tag_levels = "A") &
  theme(legend.position = "top")

if (!interactive()) {
  ggsave_default(width = 13, height = 5)
}
```

## Predictive power of ISS and IGS (precise d')

```{r}
#| label: fig-supp-3-iss-igs-pred-mem
#| fig-width: 13
#| fig-height: 8

# ISS predicts memory
p_iss_mem_rem_scatter <- visualize_scatter(
  targets::tar_read(data_iss_whole),
  targets::tar_read(mem_perf_precise) |>
    select(subj_id, dprime = dprime_rem),
  lab_perf = "Recollection",
  show_legend = TRUE
)

p_iss_mem_rem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iss_mem_dynamic_dprime_rem),
  targets::tar_read(clusters_stats_iss_mem_dynamic_dprime_rem),
  col_stat = "estimate",
  lab_stat = expression(italic(r)[ISS - "Recollection"])
)

p_iss_mem_know_scatter <- visualize_scatter(
  targets::tar_read(data_iss_whole),
  targets::tar_read(mem_perf_precise) |>
    select(subj_id, dprime = dprime_know),
  lab_perf = "Familiarity",
  col_stat = "iss"
)

p_iss_mem_know_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iss_mem_dynamic_dprime_know),
  targets::tar_read(clusters_stats_iss_mem_dynamic_dprime_know),
  col_stat = "estimate",
  lab_stat = expression(italic(r)[ISS - "Familiarity"])
)

# IGS predicts memory
p_igs_mem_rem_scatter <- visualize_scatter(
  targets::tar_read(data_igs_whole),
  targets::tar_read(mem_perf_precise) |>
    select(subj_id, dprime = dprime_rem),
  lab_perf = "Recollection"
)

p_igs_mem_rem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_igs_mem_dynamic_dprime_rem),
  targets::tar_read(clusters_stats_igs_mem_dynamic_dprime_rem),
  lab_stat = expression(italic(r)[IGS - "Recollection"])
)

p_igs_mem_know_scatter <- visualize_scatter(
  targets::tar_read(data_igs_whole),
  targets::tar_read(mem_perf_precise) |>
    select(subj_id, dprime = dprime_know),
  lab_perf = "Familiarity"
)

p_igs_mem_know_dynamic <- visualize_dynamic(
  targets::tar_read(stats_igs_mem_dynamic_dprime_know),
  targets::tar_read(clusters_stats_igs_mem_dynamic_dprime_know),
  lab_stat = expression(italic(r)[IGS - "Familiarity"])
)

(p_iss_mem_rem_scatter | p_iss_mem_rem_dynamic) /
  (p_iss_mem_know_scatter | p_iss_mem_know_dynamic) /
  (p_igs_mem_rem_scatter | p_igs_mem_rem_dynamic) /
  (p_igs_mem_know_scatter | p_igs_mem_know_dynamic) +
  plot_layout(guides = "collect") &
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")

if (!interactive()) {
  ggsave_default(width = 13, height = 8)
}
```

## Comparison of ISS and IGS

Here we compare the predictive power of ISS and IGS on memory performance. We use linear regression to model the relationship between ISS/IGS and memory performance, and we compare the models using adjusted R-squared.

Note we decided that the figures will be only included in the supplementary materials.

```{r}
#| label: fig-supp-4-iss-igs-comparison
#| fig-width: 13
#| fig-height: 8

p_iss_comp <- visualize_data_distr(
  targets::tar_read(data_iss_whole),
  targets::tar_read(stats_iss_whole),
  targets::tar_read(iss_comparison),
  show_legend = TRUE
)

p_iss_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iss_dynamic),
  targets::tar_read(clusters_stats_iss_dynamic),
  col_stat = "estimate",
  lab_stat = "ISS"
)

p_igs_comp <- visualize_data_distr(
  targets::tar_read(data_igs_whole),
  targets::tar_read(stats_igs_whole),
  targets::tar_read(igs_comparison)
)

p_igs_dynamic <- visualize_dynamic(
  targets::tar_read(stats_igs_dynamic),
  targets::tar_read(clusters_stats_igs_dynamic),
  col_stat = "estimate",
  lab_stat = "IGS"
)

p_gss_whole <- visualize_mantel(
  targets::tar_read(patterns_group_whole),
  targets::tar_read(pattern_semantics),
  targets::tar_read(stats_gss_whole),
  "Group Averaged Neural Representation",
  "Semantic Resprentation"
)

p_gss_dynamic <- visualize_dynamic(
  targets::tar_read(stats_gss_dynamic),
  targets::tar_read(clusters_stats_gss_dynamic),
  col_stat = "statistic",
  lab_stat = "GSS"
)

(p_iss_comp | p_iss_dynamic) /
  (p_igs_comp | p_igs_dynamic) /
  (p_gss_whole | p_gss_dynamic) +
  plot_layout(guides = "collect") &
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")

if (!interactive()) {
  ggsave_default(width = 13, height = 10)
}
```

## Mediation analysis of ISS and IGS on memory performance

First, we investigate the predictive power of ISS on memory performance after controlling for the group averaged representation. We use linear regression to model the relationship between ISS and memory performance, and we compare the models with and without IGS as a covariate.

```{r}
#| label: fig-3-part-1-iss-partial-group
#| eval: false

p_compare_iss_partial <- visualize_comp_partial(
  targets::tar_read(iss_comp_partial),
  comp_labels = c("ISS", "ISS|G")
)

p_iss_partial_scatter <- visualize_scatter(
  targets::tar_read(data_iss_partial_whole),
  targets::tar_read(mem_perf),
  lab_stat = "ISS|G",
  col_stat = "iss",
  show_legend = TRUE
)

p_iss_partial_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iss_partial_mem_dynamic),
  targets::tar_read(clusters_stats_iss_partial_mem_dynamic),
  col_stat = "estimate",
  lab_stat = expression(italic(r)["ISS|G" - "d'"])
)

p_compare_predictions <- visualize_comp_preds(
  `IGS + ISS|G` = targets::tar_read(lm_mem_igs_iss_partial),
  `ISS|G` = targets::tar_read(lm_mem_iss_partial)
)
```

Second, we investigate the mediation effect of IGS on the relationship between ISS and memory performance. We use structural equation modeling (SEM) to model the mediation effect, and we visualize the mediation diagram.

```{r}
#| label: fig-3-part-2-iss-igs-med
#| eval: false

path_med_diagram <- fs::path("figures", "mediation_iss_igs_mem.png")
diagram_iss_igs <- targets::tar_read(fit_med_iss_igs_dprime) |>
  visualize_mediation(
    lab_x = LAB_ISS_MED,
    lab_m = LAB_IGS_MED,
    lab_y = LAB_MEM_MED
  )
diagram_iss_igs |>
  DiagrammeRsvg::export_svg() |>
  charToRaw() |>
  rsvg::rsvg_png(path_med_diagram, width = 1000)
p_mediation <- png::readPNG(path_med_diagram, native = TRUE)
```

```{r}
#| label: fig-3-iss-igs-mem
#| eval: false
#| column: page
#| fig-width: 13
#| fig-height: 8

design <- "
AAAAABBBBBBBBEEE
AAAAABBBBBBBBEEE
AAAAABBBBBBBBEEE
CCCCCCCCDDDDDDDD
CCCCCCCCDDDDDDDD
CCCCCCCCDDDDDDDD
"
wrap_elements(p_mediation) +
  p_compare_iss_partial +
  p_iss_partial_scatter +
  p_iss_partial_dynamic +
  p_compare_predictions +
  plot_layout(design = design, guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")
if (!interactive()) {
  ggsave_default(width = 13, height = 6)
}
```

For comparison, we also investigate the predictive power of IGS on memory performance after controlling for the semantic representation, and the mediation effect of ISS on the relationship between IGS and memory performance.

```{r}
#| label: fig-supp-X-part-1-igs-partial-semantic

p_compare_igs_partial <- visualize_comp_partial(
  targets::tar_read(igs_comp_partial),
  comp_labels = c("IGS", "IGS|S")
)

p_igs_partial_scatter <- visualize_scatter(
  targets::tar_read(data_igs_partial_whole),
  targets::tar_read(mem_perf),
  lab_stat = "IGS|S",
  col_stat = "igs",
  show_legend = TRUE
)

p_igs_partial_dynamic <- visualize_dynamic(
  targets::tar_read(stats_igs_partial_mem_dynamic),
  targets::tar_read(clusters_stats_igs_partial_mem_dynamic),
  col_stat = "estimate",
  lab_stat = expression(italic(r)["IGS|S" - "d'"])
)

p_compare_predictions <- visualize_comp_preds(
  `ISS + IGS|S` = targets::tar_read(lm_mem_iss_igs_partial),
  `IGS|S` = targets::tar_read(lm_mem_igs_partial)
)
```

```{r}
#| label: fig-supp-X-part-2-igs-iss-med
#| eval: false

path_med_diagram <- fs::path("figures", "mediation_igs_iss_mem.png")
diagram_igs_iss <- targets::tar_read(fit_med_igs_iss_dprime) |>
  visualize_mediation(
    lab_x = LAB_IGS_MED,
    lab_m = LAB_ISS_MED,
    lab_y = LAB_MEM_MED
  )
diagram_igs_iss |>
  DiagrammeRsvg::export_svg() |>
  charToRaw() |>
  rsvg::rsvg_png(path_med_diagram, width = 1000)
p_mediation <- png::readPNG(path_med_diagram, native = TRUE)
```

```{r}
#| label: fig-supp-X-igs-iss-mem
#| eval: false
#| column: page
#| fig-width: 13
#| fig-height: 8

design <- "
AAAAABBBBBBBBEEE
AAAAABBBBBBBBEEE
AAAAABBBBBBBBEEE
CCCCCCCCDDDDDDDD
CCCCCCCCDDDDDDDD
CCCCCCCCDDDDDDDD
"
wrap_elements(p_mediation) +
  p_compare_igs_partial +
  p_igs_partial_scatter +
  p_igs_partial_dynamic +
  p_compare_predictions +
  plot_layout(design = design, guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")
if (!interactive()) {
  ggsave_default(width = 13, height = 6)
}
```

## Unique and shared contributions of ISS and IGS to memory performance

Here we complement the mediation analysis with a direct variance-decomposition view. We quantify the joint, unique, and shared contributions of ISS and IGS to memory using the subject-level summaries generated with the `sum` aggregation method (`data_combined_summary_sum`) together with the corresponding precomputed commonality analysis (`ctb_model_iss_igs_dprime`, `method == "sum"`). For comparison, the partial representational measures `ISS|G` and `IGS|S` are shown in the supplementary figure below.

```{r}
#| label: fig-X-iss-igs-commonality-prepare

data_joint_sum <- targets::tar_read(data_combined_summary_sum)

fit_joint_sum <- data_joint_sum |>
  transmute(
    dprime = as.numeric(scale(dprime)),
    c_iss = as.numeric(scale(c_iss)),
    c_igs = as.numeric(scale(c_igs))
  ) |>
  lm(dprime ~ c_iss + c_igs, data = _)

stats_joint_sum <- broom::glance(fit_joint_sum) |>
  select(r.squared, adj.r.squared, statistic, p.value)

data_pred_joint_sum <- data_joint_sum |>
  mutate(
    pred_dprime = predict(lm(dprime ~ c_iss + c_igs, data = data_joint_sum))
  )

stats_pred_joint_sum <- cor.test(
  data_pred_joint_sum$pred_dprime,
  data_pred_joint_sum$dprime
) |>
  broom::tidy() |>
  prepare_corr_plotmath(name_p = "italic(p)")

params_joint_sum <- broom::tidy(fit_joint_sum, conf.int = TRUE) |>
  filter(term != "(Intercept)") |>
  mutate(
    term = recode(term, c_iss = "ISS unique", c_igs = "IGS unique"),
    term = factor(term, levels = c("ISS unique", "IGS unique")),
    p.value.signif = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      TRUE ~ ""
    )
  )

data_commonality <- targets::tar_read(ctb_model_iss_igs_dprime) |>
  mutate(
    term = recode(
      term,
      `U[c_iss]` = "ISS unique",
      `U[c_igs]` = "IGS unique",
      `C[c_igs, c_iss]` = "Shared",
      `C[c_iss, c_igs]` = "Shared"
    )
  )

data_commonality_sum <- data_commonality |>
  filter(method == "sum", term != "Total") |>
  mutate(
    term = factor(term, levels = c("ISS unique", "IGS unique", "Shared")),
    label_percent = sprintf("%.1f%%", percent),
    label_r2 = sprintf("R² = %.3f", estimate)
  )

total_r2_sum <- data_commonality |>
  filter(method == "sum", term == "Total") |>
  pull(estimate)
```

```{r}
#| label: fig-3-iss-igs-unique-shared
#| column: page
#| fig-width: 13
#| fig-height: 4.5

p_joint_pred <- data_pred_joint_sum |>
  ggplot(aes(pred_dprime, dprime)) +
  geom_point(size = 2.2, alpha = 0.75, color = "#4D4D4D", show.legend = FALSE) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    linewidth = 0.9,
    color = "black",
    fill = "grey80",
    show.legend = FALSE
  ) +
  geom_text(
    data = stats_pred_joint_sum,
    aes(x = -Inf, y = Inf, label = label),
    hjust = -0.05,
    vjust = 1.15,
    parse = TRUE,
    inherit.aes = FALSE
  ) +
  scale_x_continuous(name = "Predicted memory performance") +
  scale_y_continuous(name = "Observed memory performance")

p_joint_unique <- params_joint_sum |>
  mutate(y = conf.high + max(conf.high, na.rm = TRUE) * 0.06) |>
  ggplot(aes(term, estimate, ymin = conf.low, ymax = conf.high)) +
  geom_linerange(
    linewidth = 1.2,
    color = "#4D4D4D",
    show.legend = FALSE
  ) +
  geom_point(
    size = 3.6,
    color = "black",
    show.legend = FALSE
  ) +
  geom_text(
    aes(y = y, label = p.value.signif),
    vjust = -0.3,
    size = SIZE_LABEL
  ) +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(
    name = expression("Unique effect (" * beta * ")"),
    expand = expansion(mult = c(0, 0.12))
  ) +
  coord_cartesian(ylim = c(0, NA))

max_commonality <- max(data_commonality_sum$percent, na.rm = TRUE)
padding_commonality <- max_commonality * 0.2
if (!is.finite(padding_commonality) || padding_commonality == 0) {
  padding_commonality <- 5
}

p_joint_common <- data_commonality_sum |>
  ggplot(aes(term, percent, fill = term)) +
  geom_col(
    width = 0.65,
    color = "black",
    linewidth = 0.4,
    show.legend = FALSE
  ) +
  geom_text(
    aes(y = percent + padding_commonality * 0.12, label = label_percent),
    vjust = 0,
    size = SIZE_LABEL,
    color = "black",
    show.legend = FALSE
  ) +
  geom_text(
    aes(y = percent / 2, label = label_r2),
    size = SIZE_LABEL * 0.78,
    color = "black",
    show.legend = FALSE
  ) +
  annotate(
    "text",
    x = 2,
    y = max_commonality + padding_commonality * 0.9,
    label = sprintf("Total R² = %.2f", total_r2_sum[[1]]),
    hjust = 0.5
  ) +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(
    name = "Contribution to explained variance (%)",
    limits = c(0, max_commonality + padding_commonality),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c(
    "ISS unique" = "#808080",
    "IGS unique" = "#BDBDBD",
    "Shared" = "#D9D9D9"
  )) +
  coord_cartesian(clip = "off") +
  theme(
    panel.grid.major.x = element_blank(),
    strip.background = element_blank()
  )

(p_joint_pred | p_joint_unique | p_joint_common) +
  plot_layout(widths = c(1.15, 1, 1.1)) +
  plot_annotation(tag_levels = "A") &
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )

if (!interactive()) {
  ggsave_default(width = 13, height = 4.5)
}
```

```{r}
#| label: fig-supp-X-iss-igs-unique-partial
#| eval: false
#| fig-width: 13
#| fig-height: 8

(p_iss_partial_scatter | p_igs_partial_scatter) /
  (p_iss_partial_dynamic | p_igs_partial_dynamic) +
  plot_annotation(tag_levels = "A")

if (!interactive()) {
  ggsave_default(width = 13, height = 8)
}
```

```{r}
#| label: fig-supp-X-iss-igs-commonality-robust
#| fig-width: 11
#| fig-height: 4

robust_commonality <- data_commonality |>
  filter(term != "Total") |>
  mutate(
    term = factor(term, levels = c("ISS unique", "IGS unique", "Shared")),
    label = sprintf("%.1f%%", percent)
  )

max_commonality_robust <- max(robust_commonality$estimate, na.rm = TRUE)
padding_commonality_robust <- max_commonality_robust * 0.2
if (!is.finite(padding_commonality_robust) || padding_commonality_robust == 0) {
  padding_commonality_robust <- 0.02
}

totals_commonality <- data_commonality |>
  filter(term == "Total") |>
  transmute(
    method,
    term = factor("ISS unique", levels = c("ISS unique", "IGS unique", "Shared")),
    y = max_commonality_robust + padding_commonality_robust * 0.9,
    label = sprintf("Total R² = %.2f", estimate)
  )

robust_commonality |>
  ggplot(aes(term, estimate)) +
  geom_segment(
    aes(xend = term, y = 0, yend = estimate),
    linewidth = 1.2,
    lineend = "round",
    color = "#595959",
    show.legend = FALSE
  ) +
  geom_point(size = 3.5, color = "#595959", show.legend = FALSE) +
  geom_text(
    aes(y = estimate + padding_commonality_robust * 0.12, label = label),
    vjust = 0,
    size = SIZE_LABEL,
    color = "black",
    show.legend = FALSE
  ) +
  geom_text(
    data = totals_commonality,
    aes(x = term, y = y, label = label),
    hjust = 0,
    vjust = 0,
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +
  facet_grid(cols = vars(method)) +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(
    name = expression("Contribution to " * R^2),
    limits = c(0, max_commonality_robust + padding_commonality_robust),
    expand = expansion(mult = c(0, 0))
  ) +
  coord_cartesian(clip = "off") +
  theme(
    panel.grid.major.x = element_blank(),
    strip.background = element_blank()
  )

if (!interactive()) {
  ggsave_default(width = 11, height = 4)
}
```

# Control analysis: word shape similarity pattern

```{r}
#| label: fig-supp-5-word-shape-pattern
#| column: page
#| fig-width: 12
#| fig-height: 6

p_gws_whole <- visualize_mantel(
  targets::tar_read(patterns_group_whole),
  targets::tar_read(pattern_shapes_charsim_none),
  targets::tar_read(stats_gws_whole_charsim_none),
  "Group Averaged Neural Representation",
  "Word Shape Similarity"
)

p_gws_dynamic <- visualize_dynamic(
  targets::tar_read(stats_gws_dynamic_charsim_none),
  targets::tar_read(clusters_stats_gws_dynamic_charsim_none),
  col_stat = "statistic",
  lab_stat = "GWS",
  show_legend = TRUE
)

p_iws_mem_whole <- visualize_scatter(
  targets::tar_read(data_iws_whole_charsim_none),
  targets::tar_read(mem_perf),
  col_stat = "iws"
)

p_iws_mem_dynamic <- visualize_dynamic(
  targets::tar_read(stats_iws_mem_dynamic_charsim_none),
  targets::tar_read(clusters_stats_less_iws_mem_dynamic_charsim_none),
  col_stat = "estimate",
  lab_stat = expression(italic(r)[IWS - "d'"])
)

(p_gws_whole | p_gws_dynamic) /
  (p_iws_mem_whole | p_iws_mem_dynamic) +
  plot_layout(guides = "collect") &
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")
if (!interactive()) {
  ggsave_default(width = 12, height = 6)
}
```

# Predicting Shared Memory Content (SMC)

## Inter-Subject Pattern Similarity (ISPS)

```{r}
#| label: fig-4-isps-and-smc
#| column: page
#| fig-width: 13
#| fig-height: 5

p_isps_dist <- targets::tar_read(data_isps_whole) |>
  mutate(cca_id = factor(cca_id)) |>
  unnest(isps) |>
  ggplot(aes(cca_id, isps)) +
  ggdist::stat_slabinterval(
    aes(slab_color = cca_id, slab_fill = cca_id),
    slab_alpha = 0.4,
    side = "both"
  ) +
  geom_hline(
    aes(yintercept = isps_baseline),
    targets::tar_read(summary_isps_whole_permuted) |>
      summarise(isps_baseline = mean(isps_mean), .by = cca_id) |>
      mutate(cca_id = factor(cca_id)),
    linetype = "dotted"
  ) +
  scale_x_discrete(name = NULL, labels = \(x) paste0("C", x)) +
  scale_y_continuous(name = "ISPS") +
  scale_color_components(
    aesthetics = c("slab_color", "slab_fill"),
    guide = "none"
  )

# p_isps_dynamic <- visualize_dynamic(
#   targets::tar_read(stats_isps_dynamic) |>
#     mutate(
#       ymax = isps_mean + isps_se,
#       ymin = isps_mean - isps_se
#     ),
#   col_stat = "isps_mean",
#   lab_stat = "ISPS",
#   col_cis = c("ymin", "ymax")
# )

# the cluster based permutation test is not useful (maybe we need TFCE)
p_isps_clusters <- visualize_dynamic(
  targets::tar_read(stats_isps_dynamic) |>
    mutate(
      ymax = isps_mean + isps_se,
      ymin = isps_mean - isps_se
    ),
  targets::tar_read(clusters_stats_isps_dynamic),
  col_stat = "isps_mean",
  lab_stat = "ISPS",
  col_cis = c("ymin", "ymax")
)

p_isps_smc <- visualize_mantel_dist(
  targets::tar_read(data_isps_smc_whole),
  targets::tar_read(stats_isps_smc_whole),
  expression(italic(r)[ISPS - SMC]),
  show_legend = TRUE
)

p_isps_smc_dynamic <- visualize_dynamic(
  targets::tar_read(stats_isps_smc_dynamic),
  targets::tar_read(clusters_stats_isps_smc_dynamic),
  col_stat = "statistic",
  lab_stat = expression(italic(r)[ISPS - SMC])
)

p_isps_dist +
  p_isps_clusters +
  p_isps_smc +
  p_isps_smc_dynamic +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

if (!interactive()) {
  ggsave_default(width = 13, height = 5)
}
```

```{r}
#| label: fig-supp-6-isps-smc-partial
#| column: page
#| fig-width: 13
#| fig-height: 7

p_isps_smc_partial_memory <- visualize_mantel_dist(
  targets::tar_read(data_isps_smc_partial_ability_whole),
  targets::tar_read(stats_isps_smc_partial_ability_whole),
  expression(italic(r)["ISPS|Mem" - SMC]),
  show_legend = TRUE
)

p_isps_smc_partial_memory_dynamic <- visualize_dynamic(
  targets::tar_read(stats_isps_smc_partial_ability_dynamic),
  targets::tar_read(clusters_stats_isps_smc_partial_ability_dynamic),
  col_stat = "statistic",
  lab_stat = expression(italic(r)["ISPS|Mem" - SMC])
)

p_isps_smc_partial_group_memory <- visualize_mantel_dist(
  targets::tar_read(data_isps_smc_partial_group_ability_whole),
  targets::tar_read(stats_isps_smc_partial_group_ability_whole),
  expression(italic(r)["ISPS|(GRSM, Mem)" - SMC])
)

p_isps_smc_partial_group_memory_dynamic <- visualize_dynamic(
  targets::tar_read(stats_isps_smc_partial_group_ability_dynamic),
  targets::tar_read(clusters_stats_isps_smc_partial_group_ability_dynamic),
  col_stat = "statistic",
  lab_stat = expression(italic(r)["ISPS|(GRSM, Mem)" - SMC])
)

p_isps_smc_partial_semantic_memory <- visualize_mantel_dist(
  targets::tar_read(data_isps_smc_partial_semantic_ability_whole),
  targets::tar_read(stats_isps_smc_partial_semantic_ability_whole),
  expression(italic(r)["ISPS|(Sem, Mem)" - SMC])
)

p_isps_smc_partial_semantic_memory_dynamic <- visualize_dynamic(
  targets::tar_read(stats_isps_smc_partial_semantic_ability_dynamic),
  targets::tar_read(clusters_stats_isps_smc_partial_semantic_ability_dynamic),
  col_stat = "statistic",
  lab_stat = expression(italic(r)["ISPS|(Sem, Mem)" - SMC])
)

(p_isps_smc_partial_memory | p_isps_smc_partial_memory_dynamic) /
  (p_isps_smc_partial_group_memory | p_isps_smc_partial_group_memory_dynamic) /
  (p_isps_smc_partial_semantic_memory |
    p_isps_smc_partial_semantic_memory_dynamic) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")

if (!interactive()) {
  ggsave_default(width = 13, height = 7)
}
```

## Neural Synchronization

```{r}
#| label: sync-and-mem
#| column: page
#| fig-width: 13
#| fig-height: 6.5
#| eval: false

targets::tar_load(sync_inter_intra)
summary_sync <- sync_inter_intra |>
  summarise(
    broom::tidy(t.test(sync)),
    .by = c(cca_id, type)
  ) |>
  rstatix::adjust_pvalue() |>
  rstatix::add_significance(
    cutpoints = c(0, 0.001, 0.01, 0.05, 1),
    symbols = c("***", "**", "*", "")
  )
compare_sync_p <- sync_inter_intra |>
  pivot_wider(
    id_cols = c(subj_id, cca_id),
    names_from = type,
    values_from = sync
  ) |>
  summarise(
    broom::tidy(t.test(intra, inter_ahead, paired = TRUE)),
    .by = cca_id
  ) |>
  rstatix::adjust_pvalue() |>
  rstatix::add_significance(
    cutpoints = c(0, 0.001, 0.01, 0.05, 1),
    symbols = c("***", "**", "*", "")
  ) |>
  mutate(
    start = "intra",
    end = "inter_ahead",
    y_position = max(summary_sync$conf.high) * 1.1
  )
p_sync_compare <- summary_sync |>
  ggplot(aes(type, estimate)) +
  geom_col(
    aes(color = cca_id, fill = cca_id, alpha = type),
    width = 0.75
  ) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.1) +
  geom_text(
    aes(y = conf.high, label = p.value.adj.signif),
    vjust = 0,
    size = SIZE_LABEL
  ) +
  ggsignif::geom_signif(
    data = compare_sync_p,
    aes(
      xmin = start,
      xmax = end,
      annotations = p.value.adj.signif,
      y_position = y_position
    ),
    textsize = SIZE_LABEL,
    inherit.aes = FALSE,
    manual = TRUE
  ) +
  facet_grid(cols = vars(cca_id)) +
  scale_x_discrete(name = NULL, labels = c("Intra", "Inter")) +
  scale_y_continuous(
    name = "Neural Sync",
    expand = expansion(c(0, 0.1))
  ) +
  scale_color_components(aesthetics = c("fill", "color")) +
  scale_alpha_manual(
    name = NULL,
    values = c(1, 0),
    guide = "none"
  ) +
  theme(strip.text = element_blank())

sync_mem <- sync_inter_intra |>
  left_join(targets::tar_read(mem_perf), by = "subj_id") |>
  mutate(cca_id = factor(cca_id))
stats_sync_mem <- sync_mem |>
  summarise(
    broom::tidy(cor.test(sync, dprime)),
    .by = c(cca_id, type)
  ) |>
  rstatix::adjust_pvalue() |>
  rstatix::add_significance(
    cutpoints = c(0, 0.001, 0.01, 0.05, 1),
    symbols = c("***", "**", "*", "")
  ) |>
  prepare_corr_plotmath() |>
  mutate(
    x = min(sync_mem$sync),
    y = max(sync_mem$dprime) * 1.2 * (1 - 0.1 * as.integer(type))
  )

p_pred_mem <- sync_mem |>
  ggplot(aes(x = sync, y = dprime, alpha = type)) +
  geom_point(aes(color = cca_id, shape = type)) +
  geom_line(
    aes(color = cca_id),
    stat = "smooth",
    method = "lm",
    formula = y ~ x
    # linewidth = 2,
    # fullrange = TRUE
  ) +
  geom_text(
    aes(x, y, label = label),
    stats_sync_mem,
    hjust = 0,
    vjust = 1,
    parse = TRUE,
  ) +
  facet_grid(cols = vars(cca_id)) +
  scale_x_continuous(name = "Neural Sync") +
  scale_y_continuous(name = "Memory (d')") +
  scale_alpha_manual(
    name = NULL,
    values = c(1, 0.5),
    guide = "none"
  ) +
  scale_shape_manual(
    name = NULL,
    values = c(16, 1),
    labels = c("Intra", "Inter")
    # guide = "none"
  ) +
  scale_color_components(guide = "none") +
  theme(strip.text = element_blank())

p_sync_smc <- visualize_mantel_dist(
  targets::tar_read(sync_smc_whole),
  targets::tar_read(stats_sync_smc_whole),
  expression(italic(r)[Sync - SMC])
)

p_sync_smc_dynamic <- visualize_dynamic(
  targets::tar_read(stats_sync_smc_dynamic),
  targets::tar_read(clusters_stats_sync_smc_dynamic),
  col_stat = "statistic",
  lab_stat = expression(italic(r)[Sync - SMC])
)

p_sync_compare +
  p_pred_mem +
  p_sync_smc +
  p_sync_smc_dynamic +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "bottom")
ggsave("figures/sync_results.png", width = 13, height = 6.5, dpi = 300)
```

```{r}
#| label: prepare-diagram-parts
#| eval: false

set.seed(1)

# representational patterns ----
vis_pat <- function(pat) {
  corrplot::corrplot(
    pat,
    method = "color",
    outline = TRUE,
    col = corrplot::COL1("Greys"),
    tl.pos = "n",
    cl.pos = "n"
  )
}
x_indiv <- pracma::squareform(rnorm(15, 0.5, 0.25))
x_group <- pracma::squareform(rnorm(15, 0.5, 0.25))
x_sem <- pracma::squareform(rnorm(15, 0.5, 0.25))
diag(x_indiv) <- diag(x_group) <- diag(x_sem) <- 1
png("figures/diagrams/indiv_matrix.png", width = 400, height = 400)
vis_pat(x_indiv)
dev.off()
png("figures/diagrams/group_matrix.png", width = 400, height = 400)
vis_pat(x_group)
dev.off()
png("figures/diagrams/sem_matrix.png", width = 400, height = 400)
vis_pat(x_sem)
dev.off()

# word2vec embeddings ----
embedding <- as_tibble(split(rnorm(14, 0.5, 0.2), rep(1:2, each = 7))) |>
  mutate(id = seq_len(n()), label = "")
embedding[6, 1:2] <- NA
embedding$label[6] <- "…"

embedding |>
  ggplot(aes(id, 1, fill = `1`)) +
  geom_tile() +
  geom_text(aes(label = label), size = 12, vjust = 0.2) +
  scale_fill_gradient(
    low = "grey80",
    high = "grey20",
    na.value = "white",
    guide = "none"
  ) +
  coord_fixed() +
  theme_void()
ggplot2::ggsave(
  "figures/diagrams/embedding_1.png",
  width = 8,
  height = 2,
  dpi = 300
)

embedding |>
  ggplot(aes(id, 1, fill = `2`)) +
  geom_tile() +
  geom_text(aes(label = label), size = 12, vjust = 0.2) +
  scale_fill_gradient(
    low = "grey80",
    high = "grey20",
    na.value = "white",
    guide = "none"
  ) +
  coord_fixed() +
  theme_void()
ggplot2::ggsave(
  "figures/diagrams/embedding_2.png",
  width = 8,
  height = 2,
  dpi = 300
)

# neural activity ----
targets::tar_load(file_cca_y)
data_trials <- arrow::open_dataset(file_cca_y) |>
  filter(subj_id == 1, cca_id == 1, trial_id %in% 1:6) |>
  collect()
data_trials |>
  nest(.by = trial_id) |>
  mutate(
    walk2(
      data,
      trial_id,
      ~ {
        ggplot(.x, aes(time_id, y)) +
          geom_line(linewidth = 3, color = "grey") +
          scale_x_continuous(name = "Time (ms)") +
          scale_y_continuous(name = "Neural Activity") +
          theme_void()
        ggsave(
          paste0("figures/diagrams/trial_", .y, ".png"),
          width = 8,
          height = 2,
          dpi = 300
        )
      }
    )
  )

data_group <- arrow::open_dataset(file_cca_y) |>
  filter(trial_id %in% 1:2, cca_id == 1) |>
  collect() |>
  summarise(y = mean(y, na.rm = TRUE), .by = c(trial_id, time_id))
data_group |>
  nest(.by = trial_id) |>
  mutate(
    walk2(
      data,
      trial_id,
      ~ {
        ggplot(.x, aes(time_id, y)) +
          geom_line(linewidth = 3, color = "black") +
          scale_x_continuous(name = "Time (ms)") +
          scale_y_continuous(name = "Neural Activity") +
          theme_void()
        ggsave(
          paste0("figures/diagrams/group_avg_trial_", .y, ".png"),
          width = 8,
          height = 2,
          dpi = 300
        )
      }
    )
  )
```
